Generating Images From Captions\\ With Attention

### 2015-10-05 iclr-paper.tex
update intro

Generating realistic images from their descriptions is a very hard task that combines together two challenging problems of language modelling and image generation. Effectively, the model has to capture the semantic meaning expressed in the description and then use that knowledge to generate the pixel intensities of the image. Generating images from captions is a significantly harder problem than a reverse problem of generating captions from images which has recenly attracted a lot of attention from machine learning research community \citep{karpathy_captions}, \citep{xu_captions}, \citep{kiros_captions} and etc.

By using a sequence to sequence framework to approach the problem of image generation from captions, our model iteratively draws the patches on canvas, while attending to the relevant words in the description.

>>>>

Statistical natural image modelling remains a fundamental problem in computer vision and image understanding. This has motivated recent approaches in generative modelling applied to natural images by employing deep neural networks for their inference and generative components. Image generative models studied previously are often restricted to learning unconditional models of images distribution or conditioned on simple structured annotations, for example classification labels. Despite the advances in generative models, learning the highly structured natural image distribution alone in the high dimensional pixel space alone proves to be a difficult task. In real world, however, images rarely appear in isolation. They often accompanied by their unstructured textual descriptions on web pages and in books. One domain presents substantial amount of relating information of the other domain. The additional information from image and unstructured text description could be used to simplify the image modelling task.

There are two directions in learning a generative model of image and text.  One approach is to learn a text generative model conditioned on the images. Significant amount of recent works have been focusing on generating captions from images\citep{karpathy_captions}, \citep{xu_captions}, \citep{kiros_captions} and etc. The models take an image descriptor and generate unstructured texts through a recurrent decoder. By contrast, learning a generative model for image and text may also be studied by generating images correctly interpreting the text description. 
Generating high dimensional realistic images from their descriptions is a more difficult approach that combines two challenging components of language modelling and image generation. Namely, the model has to capture the semantic meaning expressed in the description and then use that knowledge to generate pixel intensities of the image. Although, the interesting high dimensional natural images lay on a small manifold that is difficult to capture, the additional text description cues of a target image may simplify the learning problem by focusing on the conditional distribution.

In this paper, we illustrate how simple sequential deep learning techniques can be used to build a conditional probabilistic model over natural image space effectively. By using a sequence to sequence framework to approach the problem of image generation from unstructured natural language captions, our model iteratively draws the patches on canvas, while attending to the relevant words in the description.
